quollr: An R Package for Visualizing 2-D Models from Non-linear Dimension Reductions in High Dimensional Space

### 2025-10-07 paper-quollr.Rmd
Setup to page width

```{r overviewhtml, eval=knitr::is_html_output(), fig.cap="algorithm", fig.pos='H'}

@@

```{r algo-step-html, eval=knitr::is_html_output(), out.width="100%", fig.height=5, fig.width=25, fig.pos='H', fig.cap="Key steps for constructing the model on the UMAP layout: (a) NLDR data, (b) hexagon bins, (c) bin centroids, (d) triangulated centroids, and (e) lifting the model into high dimensions. The `Scurve` data is shown."}

@@

```{r linkerror, echo=TRUE, eval=knitr::is_html_output(), fig.cap="Link plot showing the relationship between the NLDR layout (left) and the fitted model overlaid with the data in $7\\text{-}D$ (right)."}

@@

```{r, echo=TRUE, eval=knitr::is_html_output(), fig.cap="Link plot showing the relationship between the distribution of residuals (left), NLDR layout (middle) and the fitted model overlaid with the data in $7\\text{-}D$ (right)."}

@@

```{r tsne-link-limb, eval=knitr::is_html_output(), fig.cap="Link plot showing the relationship between the NLDR layout (left) and the fitted model overlaid with the data in $7\\text{-}D$ (right)."}

@@

```{r tsne-link-limb-best, eval=knitr::is_html_output(), fig.cap="Link plot showing the relationship between the NLDR layout (left) and the fitted model overlaid with the data in $7\\text{-}D$ (right)."}

>>>>

```{r overviewhtml, eval=knitr::is_html_output(), fig.cap="algorithm", fig.pos='H', layout = "l-page"}

@@

```{r algo-step-html, eval=knitr::is_html_output(), out.width="100%", fig.height=5, fig.width=25, fig.pos='H', fig.cap="Key steps for constructing the model on the UMAP layout: (a) NLDR data, (b) hexagon bins, (c) bin centroids, (d) triangulated centroids, and (e) lifting the model into high dimensions. The `Scurve` data is shown.", layout = "l-page"}

@@

```{r linkerror, echo=TRUE, eval=knitr::is_html_output(), fig.cap="Link plot showing the relationship between the NLDR layout (left) and the fitted model overlaid with the data in $7\\text{-}D$ (right).", layout = "l-page"}

@@

```{r, echo=TRUE, eval=knitr::is_html_output(), fig.cap="Link plot showing the relationship between the distribution of residuals (left), NLDR layout (middle) and the fitted model overlaid with the data in $7\\text{-}D$ (right).", layout = "l-page"}

@@

```{r tsne-link-limb, eval=knitr::is_html_output(), fig.cap="Link plot showing the relationship between the NLDR layout (left) and the fitted model overlaid with the data in $7\\text{-}D$ (right).", layout = "l-page"}

@@

```{r tsne-link-limb-best, eval=knitr::is_html_output(), fig.cap="Link plot showing the relationship between the NLDR layout (left) and the fitted model overlaid with the data in $7\\text{-}D$ (right).", layout = "l-page"}
